\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
possible -> supported.
comma before etc and full stop after

This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from all the possible geometry input files formats.

@@

%%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
logical expression in disjunctive normal form.

>>>>

This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from all the supported  geometry input files formats.

@@

%%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
logical expression in disjunctive normal form.
